---
title: "Template Title"
author: "Lorenz Alban Oehler"
date: "The Date"
output:
  html_document:
    theme: flatly      
    toc: true          
    toc_float: true    
    toc_depth: 4       
    highlight: tango   
    df_print: paged    
    css: styles.css 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This script serves as a playing ground to figure out which variables serve best to build a good model, to predict our dependend variable. 

```{r}
library(reactable)
library(sf)
library(data.table)
remove(list = ls())
library(tidyverse)
```

```{r}
sample <- readRDS("../../data_raw/samples/sample_for_model_building.RDS")
```
```{r}
## how many colums are there
sample %>% dim()
```

we have 164 variables

# selection

## filter for NAs
filter for variables which have lots of NAs 

```{r}
dat_table_nas <- tibble(
  "colnames" = colnames(sample),
  "pecentageNAs" = sapply(
    sample,
    FUN = function(x)
      round(mean(is.na(x)), 3)
  )
)

hist(dat_table_nas$pecentageNAs,breaks = 40)
reactable(dat_table_nas,filterable = T,compact = T,defaultPageSize = 15)
```
## filter below .8
because we need values to actually contain information we will only take a look at the variables, that have at least 50% not NA

```{r}
### leads to deletion of 
(dat_table_nas$pecentageNAs > .5) %>% sum

## how many 
dat_selection <- dat_table_nas %>% filter(pecentageNAs < .5)
```

# model with single predictor
In the next step i will run just a single model to get a rough idea of how well two variables are connected and could be used for prediction

Because of simplicity I will just ran a numeric and factorial model for each variable. I will exclude the variables which have way to many levels (over 500).
This loop either jumps the variable, if the variable only has 1 level or over 500.

```{r}

```

```{r}
list_variables <- dat_selection$colnames

dat_ko_variables <- data_frame(
  "variable" = character(),
  "r_squared_num" = character(),
  "p_value_num" = character(),
  "r_squared_factor" = character(),
  "p_value_factor" = character(),
  "n_fac_lelves" = character(),
  "min" = character(),
  "qnt_1st" = character(),
  "median" = character(),
  "mean" = character(),
  "qnt_3rd" = character(),
  "max" = character(),
  "NA_percentage" = character()
)

for (i in 1:length(list_variables)) {
  tmp_object <- list_variables[i]
  tmp_variable_num <- sample[[tmp_object]]
  tmp_variable_fac <- tmp_variable_num %>% as.factor()
  tmp_length_variable <- table(tmp_variable_fac) %>% length()
  
  print(paste0("now doing number: ", i))
  
  ### dont run model if more then 15 factor
  if (tmp_length_variable > 500) {
    tmp_data <- data_frame(
      "variable" = tmp_object,
      "r_squared_num" = NA,
      "p_value_num" = NA,
      "r_squared_factor" = NA,
      "p_value_factor" = NA,
      "n_fac_lelves" = tmp_length_variable,
      "min" = summary(tmp_variable_num)[1],
      "qnt_1st" = summary(tmp_variable_num)[2],
      "median" = summary(tmp_variable_num)[3],
      "mean" = summary(tmp_variable_num)[4],
      "qnt_3rd" = summary(tmp_variable_num)[5],
      "max" = summary(tmp_variable_num)[6],
      "NA_percentage" = mean(is.na(tmp_variable_num))
    )
    
    dat_ko_variables <- rbind(dat_ko_variables, tmp_data)
    print("early exit, too many")
    next
    
  } else if (tmp_length_variable <= 1) {
    tmp_data <- data_frame(
      "variable" = tmp_object,
      "r_squared_num" = NA,
      "p_value_num" = NA,
      "r_squared_factor" = NA,
      "p_value_factor" = NA,
      "n_fac_lelves" = tmp_length_variable,
      "min" = summary(tmp_variable_num)[1],
      "qnt_1st" = summary(tmp_variable_num)[2],
      "median" = summary(tmp_variable_num)[3],
      "mean" = summary(tmp_variable_num)[4],
      "qnt_3rd" = summary(tmp_variable_num)[5],
      "max" = summary(tmp_variable_num)[6],
      "NA_percentage" = mean(is.na(tmp_variable_num))
    )
    
    dat_ko_variables <- rbind(dat_ko_variables, tmp_data)
    print("early exit, one or less")
    next
    
  } else {
    formula <- as.formula(paste("aestudio ~", tmp_object))
    model_num <- lm(sample$aestudio ~ tmp_variable_num)
    model_fac <- lm(sample$aestudio ~ tmp_variable_fac)
    
    r_squared_num <- summary(model_num)$r.squared
    p_value_num <- summary(model_num)$coefficients[1, 4]
    
    r_squared_factor <- summary(model_fac)$r.squared
    p_value_factor <- summary(model_fac)$coefficients[1, 4]

    tmp_data <- data_frame(
      "variable" = tmp_object,
      "r_squared_num" = r_squared_num,
      "p_value_num" = p_value_num,
      "r_squared_factor" = r_squared_factor,
      "p_value_factor" = p_value_factor,
      "n_fac_lelves" = tmp_length_variable,
      "min" = summary(tmp_variable_num)[1],
      "qnt_1st" = summary(tmp_variable_num)[2],
      "median" = summary(tmp_variable_num)[3],
      "mean" = summary(tmp_variable_num)[4],
      "qnt_3rd" = summary(tmp_variable_num)[5],
      "max" = summary(tmp_variable_num)[6],
      "NA_percentage" = mean(is.na(tmp_variable_num))
    )
    dat_ko_variables <- rbind(dat_ko_variables, tmp_data)
  }
}

```

```{r}
## convert column to numeric
dat_ko_variables$mean <- dat_ko_variables$mean %>% as.numeric() 

### round variables to 3 digits after 0 
dat_ko_variables <- dat_ko_variables %>%
  mutate(across(where(is.numeric), ~ round(.x, 3)))

dat_ko_variables %>% reactable(.,compact = T, filterable = T,defaultPageSize = 20)
```

```{r}
dat_ko_variables <- dat_ko_variables[order(dat_ko_variables$r_squared_factor,decreasing = T),]
```

## save as excel
For exploratory purposes I will export the data frame as an excel.   
An older version of this exists which was used to select the variables, it has the suffix _filled. 

```{r}
library(openxlsx)
write.xlsx(dat_ko_variables,"../../data_raw/2024_census/processed/dat_ko_variables_selection.xlsx")
```

# combined model

```{r}
## remove aestudio
dat_ko_variables_selection <- dat_ko_variables %>% dplyr::filter(variable != "aestudio")

### remove variables with high fac levels
dat_ko_variables_selection <- dat_ko_variables_selection[dat_ko_variables_selection$n_fac_lelves < 15,]

### remove variables with high NA-ratio
dat_ko_variables_selection <- dat_ko_variables_selection[dat_ko_variables_selection$NA_percentage < .25,]

### remove variables, which are too close conceptually
dat_ko_variables_selection <- dat_ko_variables_selection %>% filter(!variable %in%  c("p41a_nivel","p41b_curso","p41a_nivel_act","p41b_curso_act","nivel_edu"))

## delete to remove singularities
dat_ko_variables_selection <- dat_ko_variables_selection %>% filter(!variable %in%  c("p49_ocu_1d","act_eco_2d_13","p341_idiomat_cod","p51_actec_2d","p50_semp","p43_pago","v19d_celular","condact_19"))

## delete variables because very similar
dat_ko_variables_selection <- dat_ko_variables_selection %>% filter(!variable %in% c("g_edad","g_edad_bol"))

## remove because a lot of NAs
dat_ko_variables_selection <- dat_ko_variables_selection %>% filter(!variable %in% c("p45_agro","v16_desague"))

### select only first
dat_ko_variables_selection <- dat_ko_variables_selection[1:40,]

candidates <- dat_ko_variables_selection[,"variable"]

sample_candidates <- sample[,c("aestudio",candidates$variable)]

formula <- paste("aestudio ~",paste(candidates$variable,collapse =  " + " ))
formula <- formula %>% as.formula()

model <- lm(formula = formula,data = sample_candidates)
model %>% summary()

step(model,direction = "backward")
```

just runngin the step probably is not the best idea


```{r}
na_counts <- sapply(sample_candidates, function(x) sum(is.na(x)))
sort(na_counts, decreasing = TRUE)

```

```{r}
### for now this approch is not the one 
# dat_ko_variables_selection_filled<- openxlsx::read.xlsx("../../data_raw/2024_census/processed/dat_ko_variables_selection_filled.xlsx")
# 
# dat_ko_variables_selection_filled <- dat_ko_variables_selection_filled %>%
#     filter(include == "yes" | include == "decide")
# 
# sample_candidates <- sample[,dat_ko_variables_selection_filled$variable]
# formula <- paste("aestudio ~",paste(colnames(sample_candidates),collapse =  " + " ))
# formula <- formula %>% as.formula()
# 
# sample_candidates$aestudio <- sample$aestudio
# 
# model <- lm(formula = formula,data = sample_candidates)
# model %>% summary()
# 
# step(model,direction = "backward")
# 
# model_step <- lm(aestudio ~ p40_lee + gedadedu + g_edad_bol + g_edad + p42c_camina + 
#     p53_ecivil + v19c_compu + p42d_comuni + p50_catocu_13 + 
#     p42b_oir + v10_combus + v06_piso + v19e_f + v11_basura + 
#     p42_discap + p31_afiliado + v19f_inetmovil + v19e_inetfijo + 
#     p42a_ver + v03_pared + v19b_tv + v18j_lavadora + 
#     urbrur + p43_pago + v18f_refri + v15_servsan + v19h_d + 
#     v19d_celular + v19g_tvcable + v08_aguadist + v18g_micro + 
#     v17_tenencia + v18c_auto + v05_techo + p32_pueblo_per + 
#     v04_revoq + p35_lugnac + p30c_privad + p25_sexo + v18b_moto + 
#     v18h_calefon + v18i_aire + v13_habitac + p30a_public + 
#     p30d_atedom + v19h_telfijo + v18d_carreta,sample)
# 
# model_step %>% summary()

### an idea how wo copoe with NA values
# library(mice)
# library(VIM)
# 
# aggr(sample_candidates, numbers = TRUE, prop = TRUE)
# imp <- mice(sample_candidates, m = 5, maxit = 10, seed = 123)
# completed_data <- complete(imp, 1) 
# plot(imp)
```


```{r}
lm(sample$aestudio ~ sample$p26_edad + sample$p25_sexo) %>% summary

### plus occupancy
lm(sample$aestudio ~ sample$p26_edad + as.factor(sample$ocu_1d_13) + sample$p25_sexo) %>% summary

### plus rural/urban
lm(sample$aestudio ~ sample$p26_edad + as.factor(sample$ocu_1d_13) + sample$p25_sexo + sample$urbrur) %>% summary

#### 
# sample$p43_pago + sample$hh_tot_pers 
```

So a model with a relatively high R^2 without a variable with lots of levels would be this:
aestudio ~ sample\$p26_edad  + sample\$p25_sexo + sample\$urbrur + sample\$p40_lee

```{r}
lm(sample$aestudio ~ sample$p26_edad  + sample$p25_sexo + sample$urbrur + sample$p40_lee) %>% summary
```

higher Rˆ2 would be this model:
```{r}
### vs without as.factor(sample$ocu_1d_13)
lm(sample$aestudio ~ sample$p26_edad  + sample$p25_sexo + as.factor(sample$ocu_1d_13) + sample$urbrur + sample$p40_lee) %>% summary
```

For now this will do, but maybe we should think about sth else



