---
title: "Template Title"
author: "Lorenz Alban Oehler"
date: "The Date"
output:
  html_document:
    theme: flatly      
    toc: true          
    toc_float: true    
    toc_depth: 4       
    highlight: tango   
    df_print: paged    
    css: styles.css 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(cowplot)
library(sf)
```

# loading data 

```{r}
dat_MSE <- readRDS("../../data_raw/simulation/processed/df_MSE_long.RDS")
dat_estimate <- readRDS("../../data_raw/simulation/processed/df_estimates_long.RDS")

map <- read_sf("../../data_raw/shape/bol_adm_mdrt_2013/bol_admbnd_adm2_mdrt_2013_v01.shp")
map <- map %>% rename(ID_prov = ADM2_PCODE )

dat_MSE %>% filter(method != "Dir") %>% 
ggplot(.,aes(x = method,MSE)) + geom_boxplot()
```


```{r}
colo <- list(
  AP = c("#FBBF24", "#22D3EE", "#FB7185", "#E5E7EB"),
  BP = c("#E5E7EB", "#38BDF8", "#A3E635"),
  CP = c("#FACC15", "#22D3EE", "#4ADE80", "#FB923C", "#F472B6")
)
```

# MSE

## data processing

```{r}
df_MSE_agg_samples_long <- dat_MSE %>% 
  group_by(ID_prov,method) %>% 
  summarise(mean_samples = mean(MSE))

df_MSE_agg_samples_wide <- pivot_wider(
  df_MSE_agg_samples_long,
  id_cols   = ID_prov,
  names_from = method,
  values_from = mean_samples
)

colnames(df_MSE_agg_samples_wide) <- c("ID_prov","MSE_BHF_mean_samples","MSE_Dir_mean_samples","MSE_FH_mean_samples")

map <- map %>% left_join(df_MSE_agg_samples_wide,by = "ID_prov")
```


```{r}
### define styel
map_style_beamer <- theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "right",
    legend.title.position = "top",
    # legend.key.height = unit(3, "mm"),
    # legend.key.width  = unit(4, "mm"),
    legend.title = element_text(size = 9),
    # legend.text  = element_text(size = 8),
    # legend.margin = margin(0, 0, 0, 0),
    # legend.box.margin = margin(0, 0, 0, 0),
    axis.title = element_blank(),
    axis.text  = element_blank(),
    axis.ticks = element_blank(),
    axis.line  = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = NA, colour = NA),
    plot.background  = element_rect(fill = NA, colour = NA)
  )

scale_fill_mse <- function(limits, name = "Mean MSE",colours = c("#134E4A", "#2A9D8F", "#FACC15")) {
  scale_fill_gradientn(
    colours = colours,
    na.value = "#334155",
    limits = limits,
    name = name
  )
}

```

## Mean MSE
which is the MSE aggregated over all samples 

### direct vs FH vs BHF

```{r}
# global_limits <- df_MSE_agg_samples_long %>% pull(mean_samples) %>% range()
# 
# p_map <- ggplot(map) +
#   geom_sf(aes(fill = MSE_BHF_mean_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer
# 
# legend_map <- get_legend(p_map)
# 
# p1 <- ggplot(map) +
#   geom_sf(aes(fill = MSE_BHF_mean_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "BHF")
# 
# p2 <- ggplot(map) +
#   geom_sf(aes(fill = MSE_FH_mean_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "FH")
# 
# p3 <- ggplot(map) +
#   geom_sf(aes(fill = MSE_Dir_mean_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "Direct")
# 
# # plot_grid(cowplot::plot_grid(p1,p2,p3,nrow = 1),legend_map,nrow = 2,rel_widths = c(3,.2)) # two rows
# plot_grid(p1,p2,p3,legend_map,nrow = 1,rel_widths = c(1,1,1,.5))
```
### FH vs BHF

```{r}
global_limits <- df_MSE_agg_samples_long %>% filter(method!= "Dir") %>% pull(mean_samples) %>% range()

p_map <- ggplot(map) +
  geom_sf(aes(fill = MSE_BHF_mean_samples)) +
  scale_fill_mse(global_limits,colours = c("#22D3EE", "#0F172A", "#FB7185")) +
  map_style_beamer

legend_map <- get_legend(p_map)


p1 <- ggplot(map) +
  geom_sf(aes(fill = MSE_BHF_mean_samples)) +
  scale_fill_mse(global_limits,colours = c("#22D3EE", "#0F172A", "#FB7185")) +
  map_style_beamer +
  theme(legend.position = "none") +
  labs(title = "BHF")


p2 <- ggplot(map) +
  geom_sf(aes(fill = MSE_FH_mean_samples)) +
  scale_fill_mse(global_limits,colours = c("#22D3EE", "#0F172A", "#FB7185")) +
  map_style_beamer +
  theme(legend.position = "none") +
  labs(title = "FH")

MSE_mean_FH_BHF_samples_aggre <- plot_grid(p1,p2,legend_map,nrow = 1,rel_widths = c(1,1,.5))
MSE_mean_FH_BHF_samples_aggre <- ggdraw() +
  draw_label(
    "Mittlerer MSE auf provinzieller Ebene",
    # fontface = "bold",
    size = 13,
    x = 0.5,
    y = 0.98,
    hjust = 0.5,
    vjust = 1
  ) +
  draw_plot(
    plot_grid(p1, p2, legend_map,
              nrow = 1,
              rel_widths = c(1, 1, .5)),
    y = 0,
    height = 0.95
  )

MSE_mean_FH_BHF_samples_aggre

ggsave("../../output/MSE_mean_FH_BHF_samples_aggre-01.svg", 
       plot = MSE_mean_FH_BHF_samples_aggre,
       width = 6,      
       height = 4,    
       units = "in",   
       device = "svg")

ggsave("../../output/MSE_mean_FH_BHF_samples_aggre-01.png", 
       plot = MSE_mean_FH_BHF_samples_aggre,
       width = 6,      
       height = 4,    
       units = "in",   
       dpi = 300)

```


## MSE sample 1

```{r}
# dat_MSE_s1 <- dat_MSE %>% 
#   filter(sample == "001") %>% 
#   mutate(MSE_s1 = MSE)
# 
# df_MSE_s1_wide <- pivot_wider(
#   dat_MSE_s1,
#   id_cols   = ID_prov,
#   names_from = method,
#   values_from = MSE_s1
# )
# 
# colnames(df_MSE_s1_wide) <- c("ID_prov","MSE_Dir_s1","MSE_FH_s1","MSE_BFH_s1")
# 
# map <- map %>% left_join(df_MSE_s1_wide,by = "ID_prov")
```


### FH vs BHF

```{r}
# global_limits <- dat_MSE_s1 %>% filter(method != "Dir") %>% pull(MSE_s1) %>% range()
# 
# p_map <- ggplot(map) +
#   geom_sf(aes(fill = MSE_BHF_mean_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer
# 
# legend_map <- get_legend(p_map)
# 
# p1 <- ggplot(map) +
#   geom_sf(aes(fill = MSE_BFH_s1)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "BHF")
# 
# 
# p2 <- ggplot(map) +
#   geom_sf(aes(fill = MSE_FH_s1)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "FH")
# 
# MSE_mean_FH_BHF_samples_aggre <- plot_grid(p1,p2,legend_map,nrow = 1,rel_widths = c(1,1,.5))
# MSE_mean_FH_BHF_samples_aggre

```

# plotting estimates

## processing

```{r}
df_estimate_agg_samples_long <- dat_estimate %>% 
  group_by(ID_prov,method) %>% 
  summarise(mean_estimate = mean(estimate),
            var_estimate = var(estimate)
            )

df_estimate_agg_samples_wide <- pivot_wider(
  df_estimate_agg_samples_long,
  id_cols   = ID_prov,
  names_from = method,
  values_from = c(mean_estimate,var_estimate)
)

colnames(df_estimate_agg_samples_wide) <- c("ID_prov","estimate_BHF_mean_samples","estimate_Dir_mean_samples","estimate_FH_mean_samples","estimate_BHF_var_samples","estimate_Dir_var_samples","estimate_FH_var_samples")

map <- map %>% left_join(df_estimate_agg_samples_wide,by = "ID_prov")
```

### BHF vs FH vs Direct

```{r}
# global_limits <- df_estimate_agg_samples_long %>% pull(mean_estimate) %>% range()
# 
# p_map <- ggplot(map) +
#   geom_sf(aes(fill = estimate_BHF_mean_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer
# 
# legend_map <- get_legend(p_map)
# 
# 
# p1 <- ggplot(map) +
#   geom_sf(aes(fill = estimate_Dir_mean_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "Direct")
# 
# 
# p2 <- ggplot(map) +
#   geom_sf(aes(fill = estimate_FH_mean_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "FH")
# 
# p3 <- ggplot(map) +
#   geom_sf(aes(fill = estimate_BHF_mean_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "BHF")
# 
# estimate_mean_Dir_FH_BHF_samples_aggre <- plot_grid(p1,p2,p3,legend_map,nrow = 1,rel_widths = c(1,1,1,.5))
# estimate_mean_Dir_FH_BHF_samples_aggre
# ggsave("../../output/estimate_mean_Dir_FH_BHF_samples_aggre-01.svg", 
#        plot = estimate_mean_Dir_FH_BHF_samples_aggre,
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        device = "svg")
# 
# ggsave("../../output/estimate_mean_Dir_FH_BHF_samples_aggre.png", 
#        plot = estimate_mean_Dir_FH_BHF_samples_aggre,
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        dpi = 300)

```

### variance

```{r}
# global_limits <- df_estimate_agg_samples_long %>% pull(var_estimate) %>% range()
# 
# p_map <- ggplot(map) +
#   geom_sf(aes(fill = estimate_BHF_var_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer
# 
# legend_map <- get_legend(p_map)
# 
# 
# p1 <- ggplot(map) +
#   geom_sf(aes(fill = estimate_Dir_var_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "Direct")
# 
# 
# p2 <- ggplot(map) +
#   geom_sf(aes(fill = estimate_FH_var_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "FH")
# 
# p3 <- ggplot(map) +
#   geom_sf(aes(fill = estimate_BHF_var_samples)) +
#   scale_fill_mse(global_limits) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "BHF")
# 
# estimate_var_Dir_FH_BHF_samples_aggre <- plot_grid(p1,p2,p3,legend_map,nrow = 1,rel_widths = c(1,1,1,.5))
# estimate_var_Dir_FH_BHF_samples_aggre
# 
# ggsave("../../output/estimate_var_Dir_FH_BHF_samples_aggre-01.svg", 
#        plot = estimate_var_Dir_FH_BHF_samples_aggre,
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        device = "svg")
# 
# ggsave("../../output/estimate_var_Dir_FH_BHF_samples_aggre.png", 
#        plot = estimate_var_Dir_FH_BHF_samples_aggre,
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        dpi = 300)
```
# Diff to real value

## processing

```{r}
# df_var_diff_true_agg_samples_long <- dat_estimate %>% 
#   group_by(ID_prov,method) %>% 
#   summarise(mean_diff_true = mean(diff_true),
#             var_diff_true = var(diff_true))
# 
# # ggplot(dat_estimate,aes(x = method, y = diff_true, fill = diff_true))+
# #   geom_boxplot()
# 
# df_var_diff_true_agg_samples_wide <- pivot_wider(
#   df_var_diff_true_agg_samples_long,
#   id_cols   = ID_prov,
#   names_from = method,
#   values_from = c(mean_diff_true,var_diff_true)
# )
# 
# colnames(df_var_diff_true_agg_samples_wide) <- c("ID_prov","diff_true_BHF_mean_samples","diff_true_Dir_mean_samples","diff_true_FH_mean_samples","diff_true_BHF_var_samples","diff_true_Dir_var_samples","diff_true_FH_var_samples")
# 
# map <- map %>% left_join(df_var_diff_true_agg_samples_wide,by = "ID_prov")
# # colnames(map)
```

### BHF vs FH vs Direct

```{r}
# global_limits <- df_var_diff_true_agg_samples_long %>% pull(mean_diff_true) %>% range()
# 
# p_map <- ggplot(map) +
#   geom_sf(aes(fill = diff_true_Dir_mean_samples)) +
#   scale_fill_mse(global_limits,
#                  name = "mean difference to true value",
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer
# 
# legend_map <- get_legend(p_map)
# 
# 
# p1 <- ggplot(map) +
#   geom_sf(aes(fill = diff_true_Dir_mean_samples)) +
#   scale_fill_mse(global_limits,
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "Direct")
# 
# 
# p2 <- ggplot(map) +
#   geom_sf(aes(fill = diff_true_FH_mean_samples)) +
#   scale_fill_mse(global_limits,
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "FH")
# 
# p3 <- ggplot(map) +
#   geom_sf(aes(fill = diff_true_BHF_mean_samples)) +
#   scale_fill_mse(global_limits,
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "BHF")
# 
# diff_true_Dir_FH_BHF_samples_aggre <- plot_grid(p1,p2,p3,legend_map,nrow = 1,rel_widths = c(1,1,1,.5))
# diff_true_Dir_FH_BHF_samples_aggre
# 
# ggsave("../../output/diff_true_Dir_FH_BHF_samples_aggre-01.svg", 
#        plot = diff_true_Dir_FH_BHF_samples_aggre,
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        device = "svg")
# 
# ggsave("../../output/diff_true_Dir_FH_BHF_samples_aggre-01.png", 
#        plot = diff_true_Dir_FH_BHF_samples_aggre,
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        dpi = 300)

```

### BHF vs FH vs Direct Sample 1

```{r}
df_diff_true_s1_long <- dat_estimate %>% 
  filter(sample == "001") 


df_var_diff_true_agg_samples_wide <- pivot_wider(
  df_diff_true_s1_long,
  id_cols   = ID_prov,
  names_from = method,
  values_from = diff_true)

colnames(df_var_diff_true_agg_samples_wide) <- c("ID_prov","diff_true_Dir_s1","diff_true_FH_s1","diff_true_BHF_s1")

map <- map %>% left_join(df_var_diff_true_agg_samples_wide,by = "ID_prov")
# colnames(map)
```


```{r}
# global_limits <- df_diff_true_s1_long %>% pull(diff_true) %>% range()
# 
# p_map <- ggplot(map) +
#   geom_sf(aes(fill = diff_true_Dir_s1)) +
#   scale_fill_mse(global_limits,
#                  name = "sample 1 difference to true value",
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer
# 
# legend_map <- get_legend(p_map)
# 
# 
# p1 <- ggplot(map) +
#   geom_sf(aes(fill = diff_true_Dir_s1)) +
#   scale_fill_mse(global_limits,
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "Direct")
# 
# 
# p2 <- ggplot(map) +
#   geom_sf(aes(fill = diff_true_FH_s1)) +
#   scale_fill_mse(global_limits,
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "FH")
# 
# p3 <- ggplot(map) +
#   geom_sf(aes(fill = diff_true_FH_s1)) +
#   scale_fill_mse(global_limits,
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "BHF")
# 
# diff_true_Dir_FH_BHF_s1 <- plot_grid(p1,p2,p3,legend_map,nrow = 1,rel_widths = c(1,1,1,.8))
# diff_true_Dir_FH_BHF_s1
# 
# ggsave("../../output/diff_true_Dir_FH_BHF_s1-01.svg", 
#        plot = diff_true_Dir_FH_BHF_s1,
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        device = "svg")
# 
# ggsave("../../output/diff_true_Dir_FH_BHF_s1-01.png", 
#        plot = diff_true_Dir_FH_BHF_s1,
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        dpi = 300)

```

### absolute difference
```{r}
df_abs_diff_true_agg_samples_long <- dat_estimate %>% 
  group_by(ID_prov,method) %>% 
  summarise(abs_mean_diff_true = mean(abs(diff_true)),
            abs_var_diff_true = var(abs(diff_true)))

# ggplot(dat_estimate,aes(x = method, y = diff_true, fill = diff_true))+
#   geom_boxplot()

df_abs_diff_true_agg_samples_wide <- pivot_wider(
  df_abs_diff_true_agg_samples_long,
  id_cols   = ID_prov,
  names_from = method,
  values_from = c(abs_mean_diff_true,abs_var_diff_true)
)

colnames(df_abs_diff_true_agg_samples_wide) <- c("ID_prov","abs_diff_true_BHF_mean_samples","abs_diff_true_Dir_mean_samples","abs_diff_true_FH_mean_samples","abs_diff_true_BHF_var_samples","abs_diff_true_Dir_var_samples","abs_diff_true_FH_var_samples")

map <- map %>% left_join(df_abs_diff_true_agg_samples_wide,by = "ID_prov")
# colnames(map)
```

### BHF vs FH vs Direct

```{r}
# global_limits <- df_abs_diff_true_agg_samples_long %>% pull(abs_mean_diff_true) %>% range()
# 
# p_map <- ggplot(map) +
#   geom_sf(aes(fill = abs_diff_true_BHF_mean_samples)) +
#   scale_fill_mse(global_limits,
#                  name = "abs mean difference to true value",
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer
# 
# legend_map <- get_legend(p_map)
# 
# 
# p1 <- ggplot(map) +
#   geom_sf(aes(fill = abs_diff_true_Dir_mean_samples)) +
#   scale_fill_mse(global_limits,
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "Direct")
# 
# 
# p2 <- ggplot(map) +
#   geom_sf(aes(fill = abs_diff_true_FH_mean_samples)) +
#   scale_fill_mse(global_limits,
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "FH")
# 
# p3 <- ggplot(map) +
#   geom_sf(aes(fill = abs_diff_true_BHF_mean_samples)) +
#   scale_fill_mse(global_limits,
#                  colours = c("#22D3EE", "#0F172A", "#FB7185")) +
#   map_style_beamer +
#   theme(legend.position = "none") +
#   labs(title = "BHF")
# 
# abs_diff_true_Dir_FH_BHF_samples_aggre <- plot_grid(p1,p2,p3,legend_map,nrow = 1,rel_widths = c(1,1,1,.8))
# abs_diff_true_Dir_FH_BHF_samples_aggre
# 
# ggsave("../../output/abs_diff_true_Dir_FH_BHF_samples_aggre-01.svg", 
#        plot = abs_diff_true_Dir_FH_BHF_samples_aggre,
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        device = "svg")
# 
# ggsave("../../output/abs_diff_true_Dir_FH_BHF_samples_aggre-01.png", 
#        plot = abs_diff_true_Dir_FH_BHF_samples_aggre,
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        dpi = 300)
```
# other plots 

## difference true value

```{r}
tmp_dat <- dat_MSE %>% group_by(sample,method) %>% reframe(mean_MSE = mean(MSE))

tmp_dat <- tmp_dat %>%
  mutate(method = factor(method, levels = c("BHF","Dir","FH")))

distance_true_value <- tmp_dat %>% filter(method != "Dir") %>% 
ggplot(., aes(x = method, y = mean_MSE, fill = method)) +
  geom_violin(alpha = 0.8) +
  geom_line(aes(group = sample), alpha = .15)+
  geom_point(alpha = .2)+
  geom_boxplot(width = 0.1, fill="white") +  # Boxplot in der Mitte
  scale_fill_manual(values = c("#7ca982","#F05425")) +
  theme_minimal() +
  labs(title = "",
       y = "MSE",
       x = "")
distance_true_value


ggsave("../../output/MSE_violin-01.svg", 
       plot = distance_true_value,
       width = 6,      
       height = 4,    
       units = "in",   
       device = "svg")

ggsave("../../output/MSE_violin-01.png", 
       plot = distance_true_value,
       width = 6,      
       height = 4,    
       units = "in",   
       dpi = 300)

```
## difference to true value 


```{r}
df_estimate_agg_samples_long <- dat_estimate


df_estimate_long <- pivot_wider(
  dat_estimate,
  id_cols   = c(ID_prov,sample),
  names_from = c(method),
  values_from = diff_true
)

colnames(df_estimate_agg_samples_wide) <- c("ID_prov","estimate_BHF_mean_samples","estimate_Dir_mean_samples","estimate_FH_mean_samples","estimate_BHF_var_samples","estimate_Dir_var_samples","estimate_FH_var_samples")

map <- map %>% left_join(df_estimate_agg_samples_wide,by = "ID_prov")
```

```{r}

distance_true_value <- ggplot(dat_estimate,aes(x = method,y = diff_true, fill = method)) +
  geom_jitter(alpha = .01) +
  geom_violin(alpha = .8) +
  scale_fill_manual(values = c("#7ca982","#334155","#F05425")) +
  geom_boxplot(width = 0.1, fill="white") +
  labs(title = "Distance from estimates to true provincial mean",
       x = "method",
       y = "difference to true value")+
  theme_minimal()
distance_true_value


ggsave("../../output/distance_true_value-02.svg", 
       plot = distance_true_value,
       width = 6,      
       height = 4,    
       units = "in",   
       device = "svg")

ggsave("../../output/distance_true_value-02.png", 
       plot = distance_true_value,
       width = 6,      
       height = 4,    
       units = "in",   
       dpi = 300)


```


## coefficient drift

```{r}
## compare with true valu

## model drift 
lst_files <- list.files("../../data_raw/simulation/models/models_rds/",full.names = T)
lst_BHF_files <- grep(pattern = "BHF",x = lst_files,value = T)
lst_FH_files <- grep(pattern = "FH_full",x = lst_files,value = T)

list_BHF_models <- lapply(lst_BHF_files, function(x) readRDS(x))
list_FH_models <- lapply(lst_FH_files, function(x) readRDS(x))

beta_BHF_long <- do.call(
  rbind,
  lapply(seq_along(list_BHF_models), function(i) {
    beta <- list_BHF_models[[i]]$model$coefficients$fixed
    data.frame(
      sample = i,
      term   = names(beta),
      value  = as.numeric(beta),
      row.names = NULL
    )
  })
)
unique(beta_BHF_long$term)

beta_BHF_long %>% 
  # filter(term == "ocu_military") %>% 
ggplot(.,aes(x = sample, y = value, color = term)) +
  geom_line() +
  theme_classic()


```


```{r}
beta_FH_long <- do.call(
  rbind,
  lapply(seq_along(list_FH_models), function(i) {
    beta <- list_FH_models[[i]]$model$coefficients$coefficients
    data.frame(
      sample = i,
      term   = rownames(list_FH_models[[i]]$model$coefficients),
      value  = as.numeric(beta),
      row.names = NULL
    )
  })
)

# sample_001_FH$model$coefficients

ggplot(beta_FH_long,aes(x = sample, y = value, color = term)) +
  geom_line(alpha = .5) +
  theme_classic()
```

### make em pretty

```{r}
library(scales)
library(viridis)
sample_022_FH <- readRDS("../../data_raw/simulation/models/models_rds/sample_022_FH_full.rds")
# sample_022_FH$model$coefficients

fh_fixed_full <- Mean ~ mean_p26_edad + share_ocu_military + share_ocu_professional +
  share_ocu_technician + share_ocu_adminSupport + share_ocu_construction +
  share_ocu_operators + share_ocu_NaN + share_read_knowing

test <- sample_022_FH$framework$combined_data
lm(fh_fixed_full,data = test)

sample_022_BHF <- readRDS("results_batch/models_rds/sample_022_BHF.rds")

bhf_fixed_base <- aestudio ~ p26_edad + ocu_military + ocu_professional +
  ocu_technician + ocu_adminSupport + ocu_construction +
  ocu_operators + ocu_NaN + read_knowing

test <- sample_022_BHF$framework$smp_data
lm(bhf_fixed_base,data = test)


######## plot coefficients over samples ########
df_optics_BHF <- beta_BHF_long %>%
  # mutate(term_BHF = term) %>% 
  group_by(term) %>%
  summarise(
    var_wert = var(value),      # Varianz 端ber die Samples
    mean_wert = mean(value)     # optional, z.B. f端r Farbe
  )

# BHF
df_optics_BHF <- df_optics_BHF %>%
  mutate(
    term_BHF = term,
    alpha = rescale(var_wert, to = c(1, .5)),   # Alpha zwischen 0.2 und 1
    color = viridis(length(var_wert))[rank(mean_wert)]  # Farbe nach Mittelwert
  )

beta_plot <- beta_BHF_long %>%
  left_join(df_optics_BHF %>% select(term, alpha, color), by = "term")

coefficiency_consistancy_BFH <- ggplot(beta_plot, aes(x = sample, y = value, group = term, color = term)) +
  geom_path(aes(color = color),size = 1, alpha = beta_plot$alpha) +
  scale_color_identity(guide = "legend", labels = beta_plot$term, name = "Term") +
  theme_classic() +
  theme(legend.position = "none")
coefficiency_consistancy_BFH

# ggsave(filename = "../../output/coefficiency_consistancy_BFH-01.png",
#        coefficiency_consistancy_BFH,       
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        dpi = 300)
```
```{r}
### get legend
legen_map <- ggplot(beta_plot, aes(x = sample, y = value, group = term, color = term)) +
  geom_path(aes(color = color),size = 1, alpha = beta_plot$alpha) +
  scale_color_identity(guide = "legend", labels = beta_plot$term, name = "Term") +
  theme_classic() +
  theme(legend.position = "bottom")

legend <- get_legend(legen_map)
```



```{r}
########### FH ##########
df_optics_FH <- beta_FH_long %>%
  rename(term_FH = term) %>% 
  group_by(term_FH) %>%
  summarise(
    var_wert = var(value),      # Varianz 端ber die Samples
    mean_wert = mean(value)     # optional, z.B. f端r Farbe
  )

df_optics_FH$term_BHF <- str_replace_all(df_optics_FH$term_FH,pattern = "share_|mean_","")

#### do all of them have a match?
df_optics_FH$term_BHF %in% df_optics_BHF$term

### merge the two data frames
df_optics_FH <- df_optics_FH %>% left_join(df_optics_BHF[,c("term_BHF","color")])

### calculate alpha values
df_optics_FH <- df_optics_FH %>%
  mutate(
    term = term_FH,
    alpha = rescale(var_wert, to = c(1, .2)),   # Alpha zwischen 0.2 und 1
    # color = viridis(length(var_wert))[rank(mean_wert)]  # Farbe nach Mittelwert
  )

term_levels <- df_optics_FH %>%
  arrange(desc(var_wert)) %>%   # HIGH variance first
  pull(term)

beta_plot <- beta_FH_long %>%
  left_join(
    df_optics_FH %>% select(term, alpha, color),
    by = "term"
  ) %>%
  mutate(
    term = factor(term, levels = term_levels)
  )

coefficiency_consistancy_FH <- ggplot(beta_plot, aes(x = sample, y = value, group = term, color = term)) +
  geom_path(aes(color = color),size = 1, alpha = beta_plot$alpha) +
  # scale_y_continuous(trans = scales::pseudo_log_trans(base = 10)) +
  coord_cartesian(ylim = c(-100, 100)) +
  scale_color_identity(guide = "legend", labels = beta_plot$term, name = "Term") +
  theme_classic() +
  theme(legend.position = "none")

coefficiency_consistancy_FH

# ggsave(filename = "../../output/coefficiency_consistancy_FH-01.png",
#        coefficiency_consistancy_FH,       
#        width = 6,      
#        height = 4,    
#        units = "in",   
#        dpi = 300)

# cor(test %>% select(starts_with("ocu_")))


plot_grid(plot_grid(coefficiency_consistancy_BFH,legend,nrow = 2,rel_heights = c(4,1),rel_widths =),coefficiency_consistancy_FH,nrow = 1)

plot_coefficieny_drift <- plot_grid(plot_grid(coefficiency_consistancy_BFH,coefficiency_consistancy_FH),legend,nrow = 2,rel_heights = c(5,1))

ggsave(filename = "../../output/coefficieny_drift-01.png",
       plot_coefficieny_drift,
       width = 6.7,
       height = 4,
       units = "in",
       dpi = 300)

ggsave(filename = "../../output/coefficieny_drift-01.svg",
       plot_coefficieny_drift,
       width = 6.7,
       height = 4,
       device = "svg")
```



