---
title: "preprocessing data for model"
author: "Lorenz Alban Oehler"
date: "The Date"
output:
  html_document:
    theme: flatly      
    toc: true          
    toc_float: true    
    toc_depth: 4       
    highlight: tango   
    df_print: paged    
    css: styles.css 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(reactable)
library(data.table)
library(openxlsx)
```

# Introduction
The goal of this script is to transform the variables into form that is not only usable for the r lm, but also for emdi and saeTrafe. This means to convert factors into dummy coded variables. 

For now only these variables will be used: 
p26_edad, p25_sexo, ocu_1d_13, urbrur, p40_lee

To make this process also work for more than this one factor, I will first create a table in excel that maps the level to name, then will write a function in r that creates a new column var each dummy variable.

# mapping of dummys

## load in excel 
The excel file is set up in the way, that the sheet names are the names of the variable, that is being recoded with a value and a label column, every value gets its own row, if a new level contains multiple levels the respecitve values all get the same label. 

```{r}
### load in sample 
sample <- readRDS("../data_raw/samples/sample_for_model_building.RDS")

### get sheet names
sheets <- getSheetNames("../data_raw/mapping/dummy_coding.xlsx")

### look at matches 
sheets %in% colnames(sample)
```

## custom function 
This function makes it very easy to remap dummys via a tabel, which could be i.e an excel sheet, where inputs can more easily be by hand, fro grouping responses, or adding names translations etc. 

```{r}
### now does not uncesserily create REST category
fun.mappingDummyCoding <- function(column, name_variable, mapping_sheet) {

  # Determine which rows are mapped
  idx <- match(column, mapping_sheet$value)
  valid <- !is.na(idx)

  # Start with levels from mapping sheet
  levels_out <- unique(mapping_sheet$label)

  # Only add REST category if there are unmatched values
  if (any(!valid)) {
    rest_cat <- paste0(name_variable, "_Missing")
    levels_out <- c(levels_out, rest_cat)
  }

  # Initialize output matrix
  out <- matrix(
    0L,
    nrow = length(column),
    ncol = length(levels_out),
    dimnames = list(NULL, levels_out)
  )

  # Fill in dummy coding for valid matches
  if (any(valid)) {
    col_idx <- match(mapping_sheet$label[idx[valid]], levels_out)
    out[cbind(which(valid), col_idx)] <- 1L
  }

  # Fill REST category if needed
  if (any(!valid)) {
    out[!valid, rest_cat] <- 1L
  }

  as.data.frame(out)
}


```



```{r}
### defining variables 
path_excel <- "../data_raw/mapping/dummy_coding.xlsx"

### select variables which are of interst for now 
# sheets_selection <- sheets[c(1,4,5,6)]
# paste0(sheets_selection,collapse = '","')  %>% cat()
sheets_selection <- c("ocu_1d_13","p25_sexo","p40_lee","urbrur","p30b_caja","v04_revoq","v18c_auto","v18h_calefon","v12_cocina")

### initialize empy data frame
size <- nrow(sample)
dummy_coding <- data.frame(matrix(nrow = size,ncol = 0))

for(i in seq_along(sheets_selection)){
 tmp_sheet <- read.xlsx(xlsxFile = path_excel,sheet = sheets_selection[i]) 
 tmp_mapping_sheet <- tmp_sheet %>% mutate(label = paste0(prefix, label)) %>% select(value, label)
 
 tmp_col_dummy_coding <- fun.mappingDummyCoding(column = sample[[sheets_selection[i]]],
                        name_variable = sheets_selection[i],
                        mapping_sheet = tmp_mapping_sheet)
 
 dummy_coding <- cbind(dummy_coding,tmp_col_dummy_coding)
}


### add other columns 
sample_transformed <- sample %>% select(ID_prov,aestudio,p26_edad) %>% cbind(.,dummy_coding)

saveRDS(sample_transformed,"../data_raw/samples/sample_for_model_building_transformed.RDS")
```


## create 

For now the recoding of the dummy variables, always creats a rest category and a column for each level -- which does not always makes sense, thus some of the variables are deleted before being put into the equation, this is the one we will use for now. 

```{r}
# paste0(colnames(sample_transformed),collapse =  " + ") 
### delete the rest categories in some cases, and for the true bin ones, decide for one
model <- lm(aestudio ~  p26_edad + ocu_military + ocu_manager + ocu_professional + ocu_technician + ocu_adminSupport + ocu_serviceSales + ocu_agriculture + ocu_construction + ocu_operators + ocu_unskilled + ocu_NaN + ocu_1d_13_Missing + sex_male + read_knowing + read_not_knowing + read_not_specified + urbrur_urban + health_insurance_yes  + health_insurance_not_specified + p30b_caja_Missing + interior_plastered_yes + v04_revoq_Missing + car_yes + + car_not_specified + v18c_auto_Missing + water_heater_yes + water_heater_not_specified + v18h_calefon_Missing + kitchen_yes + v12_cocina_Missing, data = sample_transformed)

model %>% summary ()

model_step <- step(model,direction = "both",trace = 0)
model_step %>% summary()

model_step$call

```

# transform variables of census data

```{r}
dat <- readRDS("../data_raw/large_files/dat_preprocessing-01.RDS")

### first colums have †o be transformed
size <- nrow(dat)
dummy_coding <- data.frame(matrix(nrow = size,ncol = 0))

for(i in seq_along(sheets_selection)){
 tmp_sheet <- read.xlsx(xlsxFile = path_excel,sheet = sheets_selection[i]) 
 tmp_mapping_sheet <- tmp_sheet %>% mutate(label = paste0(prefix, label)) %>% select(value, label)
 
 tmp_col_dummy_coding <- fun.mappingDummyCoding(column = dat[[sheets_selection[i]]],
                        name_variable = sheets_selection[i],
                        mapping_sheet = tmp_mapping_sheet)
 
 dummy_coding <- cbind(dummy_coding,tmp_col_dummy_coding)
}


### add numeric values and ID col
dat_transformed <- dat %>% select(aestudio,p26_edad,ID_prov) %>% cbind(.,dummy_coding)

## save transformed census
saveRDS(dat_transformed,"../data_raw/2024_census/processed/dat_dummyCoding.RDS")
```

# calculate auxillary data for FH model 

```{r}
### calculate auxi
covariats_numeric <-c("p26_edad")

covariats_factors <- c(
  "ocu_military",
  "ocu_manager",
  "ocu_professional",
  "ocu_technician",
  "ocu_adminSupport",
  "ocu_serviceSales",
  "ocu_agriculture",
  "ocu_unskilled",
  "sex_male",
  "read_knowing",
  "urbrur_urban",
  "health_insurance_yes",
  "interior_plastered_yes",
  "v04_revoq_Missing",
  "car_yes",
  "water_heater_yes",
  "kitchen_yes"
)


dat_census_aux <- dat_transformed %>%
  group_by(ID_prov) %>%
  summarise(
    across(all_of(covariats_numeric), ~ mean(.x, na.rm = TRUE), .names = "mean_{.col}"),
    across(all_of(covariats_factors), ~ mean(.x == 1, na.rm = TRUE), .names = "share_{.col}")
  ) %>%
  ungroup()

saveRDS(dat_census_aux,"../data_raw/2024_census/processed/census_aux_data_aggregated.RDS")

```


# True aestudio for provinces for comparison 

```{r}
true_mean <- dat %>% group_by(ID_prov) %>% reframe(mean_aestudio_true = mean(aestudio,na.rm = T))
saveRDS(true_mean,"../data_raw/2024_census/processed/true_mean_aestudio.RDS")
```